\subsection{Review}
This sprint had a big focus on researching and understanding the problem. Generally, it was successful. The Scrum Master finished the common sections for the report, while the group researched where they became more familiar with the codebase, theory, and the problem in general.

Theory-wise, the primary researched part was DBMs, since this is the more relevant to our problem of reducing clocks. This problems criteria for a solution was also given by the Product Owner, along with a few scenarios for when a clock can be reduced, with ranging difficulty.

Generally, the group did not find any elements of the problem making it seem either too much or too little to work with. The problem is naturally scalable in the sense that there are multiple scenarios for clock reduction, meaning we only need to implement the scenarios that seems doable within our capabilities and time constraint.



%Vi har fået en del content, 

%I forhold til. fællesskrivning:  Ecdar, Agile og Collaboration er done.

%Der er blevet skrevet om teori og kodebasen. 

%Teorimæssigt er. der skrevet om. TIOA og DMBs. Vi vil gerne have skrevet lidt mere om dbm (måske)? Der er skrevet om federations under dbm. Der mangler at blive skrevet om model checking

%Kodebasen er der skrevet lidt om, men nok til at informere læseren om hvor præcis klok analysen skal foregå i koden.

%Folk synes generelt, at opgaven er som vi regnede med.

%Hvor nemt er det at implementere i Rust? Vi skal have bedre overblik over kodebasen.

%Det advandcerede eksempel lyder spændende, men er mere kompliceret.

\iffalse
Mangler:
Omskriv model checking. BALINGO
Skriv om transition systems. Magnus
Define what a specification is. Magnus
Beslut om der er skrevet nok til dbm. Simon
Få review fra Martijn implementeret. Kira
Review. Loppe
\fi